Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
Added information with and without wall cuts

In addition, configurations with and without application of $WallCut(D)$ were tested. While $WallCut(D)$ was used throughout the original PICO-60 analysis because it is necessary for Acoustic Parameter, it was unknown whether or not it was required for neural networks.

@@

It is difficult to say with a high degree of confidence whether or not this is an effective discriminator, since Acoustic Parameter is not decisive on data without $WallCut(D)$. However, the lack of decisiveness observed even when accuracy was relatively high, as seen in Figure \ref{waveform_best_validation}, implies this is a suboptimal technique.

@@

@@

It became evident very quickly that a high resolution was not required to get a high accuracy relative to the ground truth data. $FourierMLP(\beta_{8})$ managed an excellent 98\% validation accuracy by this metric. Increasing the number of bands seemed initially not to provide any improvement; the best accuracy reached with $\beta_{20}$ was 93\%, and with $\beta_{40}$ it was 94\%.

@@

In all previous experimentation, $WallCut(D)$ was applied to the training and validation sets. The higher resolution demonstrated significant power when $WallCut(D)$ was not applied, and only $QualCut(MultiCut(D))$ was used. $FourierMLPWithPos(\beta_{40}, \chi)$ still managed 92\% validation accuracy. However, training on $\beta_{50,001}$, which does not incorporate any banding, improved this figure to a maximum of 97\%.

>>>>

Except where specifically mentioned, $WallCut(D)$ was not applied. This was done to test the network's ability to handle complex acoustic characteristics including resonance. There is a relatively clear-cut discrimination boundary in PICO-60, but this may not be the case in other applications.

@@

However, the lack of decisiveness observed even when accuracy was relatively high, as seen in Figure \ref{waveform_best_validation}, implies this is a suboptimal technique.

@@

$WallCut(D)$ was applied to the low-resolution Fourier transforms during early experiments (since they were used for Acoustic Parameter) to minimize the number of variables between the neural network and a proven discriminator.

@@

It became evident very quickly that, without $WallCut(D)$ a high resolution was not required to get a high accuracy relative to the ground truth data. $FourierMLP(\beta_{8})$ managed an excellent 98\% validation accuracy by this metric. Increasing the number of bands, even up to $FourierMLPWithPos(beta_{20}, \chi)$, did not improve the results; accuracy only reached 94\%.

@@

The higher resolution demonstrated significant power when $WallCut(D)$ was not applied, and only \\ $QualCut(MultiCut(D))$ was used. $FourierMLPWithPos(\beta_{20}, \chi)$ achieved only 92\% accuracy (2 percentage points lower than the same configuration without $WallCut(D)$). $FourierMLPWithPos(\beta_{40}, \chi)$ also managed 92\% validation accuracy. However, training on $\beta_{50,001}$, which does not incorporate any banding, improved this figure to a maximum of 97\%.
